VariantSpark: Population Scale Clustering of Genotype Information

### 2015-08-19 doc/publications/journal2014/paper.tex
added table2

>>>>

\label{scalingcomparison}
\begin{table}[h!]
\caption{The resources consumption on different subsets of the entire autosome (chromosomes 1-22). Memory specified is memory allocated to each executor.}
      \begin{tabular}{|c|ccc|ccc|c|c|}
        \hline
           Portion &  \multicolumn{3}{ c |}{Pre-processing} & \multicolumn{3}{ c |}{Clustering}  \\
& executors & memory & time  & executors & memory & time \\
  \hline
20\%		& 64	& 2	& 11min 53sec	& 64	& 6	& 1hr 10min	\\
40\%		& 64	& 2	& 19min 9sec	& 64	& 12	& 2hr 19min	\\
60\%		& 64	& 2	& 67min		& x	& 32	& x	\\
100\%	& 64	& 2	& 40min 48sec	& x	& 24	& 14hr 44min	\\
  \hline
      \end{tabular}
\end{table}
